### 2014-11-12 heat-transfer.tex
Remove unneeded subfloats.
some rewording

In the Heat Transfer algorithm~(HT), we have a graph where heat values are
exchanged between nodes. The program stops when the new heat values of every node are
$\delta = |H_i - H_{i-1}| \le \epsilon$. The algorithm works
asynchronously since heat values can be updated by using new partial information
coming from neighbor nodes. This increases parallelism since nodes do not need
to synchronize between iterations.

@@

new-heat(A, New, Old)
fabs(New - Old) <= epsilon
   -o {B | !edge(A, B) |
         new-neighbor-heat(B, A, New)}.
\end{Verbatim}
  \scap{code:ht}{Coordination code for the Heat Transfer program. We updated the first rule
     to increase the priority of neighbor nodes.  The code logic remains exactly
     the same as before, however bigger changes in heat values are now
     propagated faster.}
\end{topfig}
\normalsize

@@

To further improve locality, we split the second rule to
not send small $\delta$ values if the target node is in another
thread (Fig.~\ref{code:ht_better}). The \textbf{Local-Only/Coordinated} line in
Fig.~\ref{results:ht} shows that this new version performs better due to
improved locality, exhibiting linear scalability over the regular version.
However, this come at the price of increased errors in the computed heat values.

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5.5cm]{results/new-heat-transfer-80}}
   \end{center}
   \scap{results:ht}{Experimental results for the HT program. The coordinated version
      is, on average, 30\% faster than the regular version although it has a
      slightly worse scalability due to a reduction in work available.}
\end{topfig}

>>>>

In the Heat Transfer algorithm~(HT), we have a graph where heat values
are exchanged between nodes. The program stops when the new heat
values of every node are $\delta = |H_i - H_{i-1}| \le \epsilon$. The
algorithm works asynchronously, i.e., heat values are updated using
information as it arrives from neighboring nodes. This increases
parallelism since nodes do not need to synchronize between iterations.

@@

new-heat(A, New, Old)
fabs(New - Old) <= epsilon
   -o {B | !edge(A, B) |
         new-neighbor-heat(B, A, New)}.
\end{Verbatim}
  \scap{code:ht}{Coordination code for the Heat Transfer program. The
      first rule now increases the priority of neighbor nodes.  The
      logic remains the same as before, however bigger
      changes in heat are now propagated faster.}
\end{topfig}
\normalsize

@@

To further improve locality, we split the second rule to avoid sending
small $\delta$ values if the target node is in another thread
(Fig.~\ref{code:ht_better}). The \textbf{Local-Only/Coordinated} line
in Fig.~\ref{results:ht} shows that this performs better due to
improved locality, exhibiting linear scalability over the regular
version.  However, this come at the price of increased errors in the
computed heat values.

@@

\begin{topfig}
   \begin{center}
      \includegraphics[width=5.5cm]{results/new-heat-transfer-80}
   \end{center}
   \scap{results:ht}{Experimental results for the HT program. The coordinated version
      is, on average, 30\% faster than the regular version although it has a
      slightly worse scalability due to a reduction in work available.}
\end{topfig}
